---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rtcassignment

<!-- badges: start -->
<!-- badges: end -->

The goal of rtcassignment is to assign output classes (Perfect ID, Genus Group, New Taxonomic Group, etc) to microbial isolates based on MALDI-TOF Real-Time Classification (RTC). This package takes the result table in a text file format, applies predetermined logic for processing those results and assignes classes, and tabulates the assignment.

What this program does:  
Step1: Accepts the raw data and cleans it up.  
Step2: Creates a flat file (each id on one line). This is the intermed file object.  
Step3: Uses part of the intermediate file as final input, to generate the result file, based on logic provided.  
Step4: Writes a text file as output with the results.  

Computational Requirements
Note this program is written for easy implementation, not speed.  
Also it uses base R code, no libraries, so can be run on any machine with R installed.  

## Installation

You can install the development version of this package from [GitHub](https://github.com/cm0109) with:

```{r install, eval=FALSE}
install.packages("devtools")
devtools::install_github("cm0109/rtcassignment")
```

## Example

This is a basic example which shows you how to use this package, using the provided example data ("example_data.txt"). 
The output will be saved in a text file named "example_assignment.txt" with this code.

```{r example, eval=FALSE}
library(rtcassignment)
rtc_to_results("inst/extdata/example_data.txt", "example_assignment.txt")
```
